A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-11-21 paper.tex
Now fits in 6 pages

We measured energy consumption associated with the transmission of 
these time-series by ``replaying" the time-series after loading them as 
a byte array in Neblina. We measured the current every 500~ms. We also 
measured the max and average latency resulting from compression in the 
data stream.

@@

The choice of an appropriate norm should not be underestimated. Some 
situations might be better described with the Euclidean norm than with 
the infinity norm, such as the ones involving position or movement 
measures. Using the infinity norm instead of the Euclidean would lead 
to important error differences, proportional to $\sqrt{n}$ in dimension 
$n$. A better algorithm to detect the intersection of n-balls in our 
context would improve the efficiency of 
LTC in dimension $n$ for arbitrary norms. Investigating other norms, in 
particular the 1-norm, would be relevant too.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio.bib}
\end{document}

>>>>

We measured energy consumption associated with the transmission of 
these time-series by ``replaying" the time-series after loading them as 
a byte array in Neblina. We measured the current every 500~ms. We also 
measured the max and average latency resulting from compression.

@@

The choice of an appropriate norm should not be underestimated. Some 
situations might be better described with the Euclidean norm than with 
the infinity norm, such as the ones involving position or movement 
measures. Using the infinity norm instead of the Euclidean would lead 
to important error differences, proportional to $\sqrt{n}$ in dimension 
$n$. Investigating other norms, in 
particular the 1-norm, would be relevant too.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio.bib}
